Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-07-29 extended_catalog/paper/extended_catalog.tex
better legedn

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{summary_plots/hess_seds.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v2/plot_seds/plot_seds.py
    \end{center}
    \caption{
    }\label{hess_seds}
  \end{figure}

>>>>

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{summary_plots/hess_seds.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/2FGL/seds/v2/plot_seds/plot_seds.py
    \end{center}
    \caption{
    The spectral energy distribution of four the extended sources
    associated with extended \tev sources.  The black points
    with circular markers are the LAT data points. The red points
    with dashed markers are H.E.S.S points of associated sources.
    Figure~\ref{hess_seds}a shows the \gev SED of 2FGL J1615.0-5051
    and \tev SED of HESS J1616-508.  Figure~\ref{hess_seds}b shows
    the \gev SED of 2FGL J1615.2-5138 and \tev SED of HESS J1614-518
    Figure~\ref{hess_seds}c shows the \gev SED of 2FGL J1632.4-4753c
    and \tev SED of HESS J1634-472 Figure~\ref{hess_seds}d shows the
    \gev SED of 2FGL J1837.3-0700c and \tev SED of HESS J1837-069.
    The H.E.S.S. data points are from (\cite{hess_plane_survey}).
    Both LAT and H.E.S.S. spectral errors are systematic only.
    }\label{hess_seds}
  \end{figure}
